%% Master CV - Mukesh Vemulapalli
%% Comprehensive overview of competencies, experience, and achievements.
%% Use as a master reference when tailoring role-specific CVs.
%% Compile with: lualatex main_example.tex

\documentclass[11pt,a4paper,sans]{moderncv}
\moderncvstyle{banking}
\moderncvcolor{blue}

\renewcommand*{\firstnamestyle}[1]{{\fontsize{34}{36}\bfseries\upshape\color{color1}#1}}
\renewcommand*{\lastnamestyle}[1]{{\fontsize{34}{36}\bfseries\upshape\color{color1}#1}}
\renewcommand*{\sectionstyle}[1]{{\sectionfont\color{color1}#1}}

\usepackage[utf8]{inputenc}
\usepackage{needspace}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,
    urlcolor=blue,
    pdftitle={Mukesh Vemulapalli - CV},
    pdfpagemode=FullScreen,
}
\usepackage[scale=0.80]{geometry}
\usepackage{import}

\name{Mukesh}{Vemulapalli}
\address{Hyderabad, Telangana, India}{}{}
\phone[mobile]{+91 9959014266}
\email{vemulapallimukesh@gmail.com}
\extrainfo{\href{https://www.linkedin.com/in/mukesh-vemulapalli-93a259261}{LinkedIn}, \href{https://github.com/Mukku27}{GitHub}, \href{https://mukeshvemulapalliportfolio.vercel.app/}{Portfolio}}

\begin{document}

\makecvtitle

\vspace{6pt}
\small{AI Engineer specializing in production LLM systems, AI agents, RAG, and recommendation pipelines. Shipped agentic commerce workflows, fine-tuned NLP models (DeBERTa F1 99.71\%), and production GenAI tools (plagiarism detector with 90\% faster evaluation). Strong in Python, PyTorch, LangChain/LangGraph, and FastAPI. Available immediately for full-time AI/ML roles (remote or India relocate).}

\section{Core Competencies}
\vspace{1pt}
\begin{itemize}
\item \textbf{LLMs \& AI Agents}: LangChain, LangGraph, LlamaIndex, CrewAI, AutoGen, RAG, prompt engineering, agent orchestration
\item \textbf{ML / Deep Learning}: PyTorch, TensorFlow, Keras, Scikit-learn, NLP, fine-tuning, evaluation (F1, ROC-AUC)
\item \textbf{Production ML}: FastAPI, Flask, Docker, data ingestion, feature pipelines, model deployment
\item \textbf{Data \& Retrieval}: NumPy, Pandas, MySQL, MongoDB, Pinecone, Streamlit
\item \textbf{Languages \& Cloud}: Python (primary), C/C++, JavaScript; AWS, Google Cloud; Git
\end{itemize}

\section{Professional Experience}
\vspace{3pt}
\begin{itemize}

\needspace{5\baselineskip}
\item{\cventry{Aug 2025--Mar 2026}{AI Engineer (Intern)}{Blotout}{Fremont, CA (Remote)}{}{\vspace{1pt}
\begin{itemize}
    \item Built and optimized AI pipelines for EvoAI: hyper-personalized recommendations, predictive search, and dynamic product ranking.
    \item Developed agentic workflows for real-time order tracking, delayed-shipment alerts, automated ticket creation, and live-agent handoff.
    \item Implemented AI-driven personalization for contextual pricing, promo-code recommendations, and behavior-based suggestions.
    \item Improved data ingestion and feature-engineering pipelines for recommendation engines and LLM-powered shopping agents.
\end{itemize}}}

\vspace{3pt}

\needspace{5\baselineskip}
\item{\cventry{Jan 2025--Jul 2025}{AI Engineer (Intern)}{Amberley Tech}{Remote, India}{}{\vspace{1pt}
\begin{itemize}
    \item Built and deployed Bittensor subnets including a Whisper-based audio caption subnet with miner-validator architecture.
    \item Fine-tuned DeBERTa for AI vs.\ human text classification (F1 99.71\%, ROC AUC 99.96\%) under adversarial conditions.
    \item Created a multi-agent content-generation system that publishes long-form articles to Arweave.
    \item Engineered an Ethereum MCP server in Python for real-time AI agent interaction with on-chain data.
\end{itemize}}}

\vspace{3pt}

\needspace{5\baselineskip}
\item{\cventry{Aug 2024--Dec 2024}{AI Intern}{Cloud Counselage Pvt.\ Ltd.}{Remote, India}{}{\vspace{1pt}
\begin{itemize}
    \item Developed an AI Code Plagiarism Detector for IAC project reviews; reduced evaluation time by 90\%; deployed to production.
    \item Fine-tuned LLaMA 3.2, Mistral, and Phi-3; built AI agents and optimized preprocessing for deployment.
\end{itemize}}}

\vspace{3pt}

\needspace{5\baselineskip}
\item{\cventry{Jul 2024}{LLM Engineer (Contract)}{Sentient Matters}{Remote, India}{}{\vspace{1pt}
\begin{itemize}
    \item Developed a banking helpline bot with Llama-2; fine-tuned for banking; automated support tasks and shipped to production.
\end{itemize}}}

\end{itemize}

\section{Selected Projects}
\vspace{1pt}
\begin{itemize}
\item \textbf{LLM Trading Agent}: Autonomous crypto trading with CoT LLMs, NumPy/Numba indicators, asyncio/ccxt, Streamlit P\&L dashboard.
\item \textbf{DeBERTa Fine-Tuning}: Multi-GPU FP16 training pipeline for human vs.\ AI text classification with rigorous evaluation.
\item \textbf{AI Inventory System}: Gemini Pro + PandasAI NL-to-SQL analytics with Streamlit/SQLite/Plotly reporting agents.
\end{itemize}

\section{Education}
\vspace{1pt}
\begin{itemize}
\needspace{5\baselineskip}
\item{\cventry{Jul 2022--May 2026}{B.Tech in Electronics and Communications Engineering}{RGUKT Nuzvid}{Nuzvid, India}{}{}}
\end{itemize}

\section{Languages}
\vspace{1pt}
\begin{itemize}
\item Telugu (native), English (professional), Hindi (professional).
\end{itemize}

\section{Honors and Awards}
\vspace{1pt}
\begin{itemize}
\item \textbf{Top 5} -- VLSI Design Contest, VLSI Design Conference 2025 (Museum Guide Bot, NXP i.MX RT117H).
\item \textbf{Finalist} -- Avishkaar Season 2 (AI Travel Assistant).
\item \textbf{Top 10} -- NXP AIM Regional Finale (autonomous car, Gazebo/ROS/CV).
\item \textbf{Top 2,000 AI builders in India} -- Y Combinator Startup School (April 2026).
\end{itemize}

\section{References}
\vspace{1pt}
\begin{itemize}
\item{Available upon request.}
\end{itemize}

\end{document}
